### 2022-07-26 src/text/1-introduction.tex
Minor fixes

@@

\begin{figure}[t]
	\centering
	\includegraphics[height=0.5\textwidth,
		angle=270]{static/gammapy-big-picture} \caption{ Gammapy is a Python package
		for high-level gamma-ray data analysis. Using event lists, exposures and point
		spread functions as input you can use it to generate science results such as
		images, spectra, light curves or source catalogs. So far it has been used to
		simulate and analyse H.E.S.S., CTA,  and \textit{Fermi}-LAT data. As demonstrated
		by several studies, it will also be applied to e.g., VERITAS, MAGIC or HAWC data
		in the future. }
	\label{fig:big-picture}

\end{figure}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[height=\textwidth, angle=270]{static/gammapy-big-picture}
    \caption{ Gammapy is a Python package
		for high-level gamma-ray data analysis. Using event lists, exposures and point
		spread functions as input you can use it to generate science results such as
		images, spectra, light curves or source catalogs. So far it has been used to
		simulate and analyse H.E.S.S., CTA,  and \textit{Fermi}-LAT data. As demonstrated
		by several studies, it will also be applied to e.g., VERITAS, MAGIC or HAWC data
		in the future. }
	\label{fig:big-picture}

\end{figure*}

@@

### 2022-07-26 src/text/2-package-subsections/makers.tex
Update figures
Minor fixes

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
	\import{code-examples/generated/}{gp_makers}

	\caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
		\code{MapDataset}. All \code{Maker} classes take
        the configuration on initialisation of the class.
    }
	\label{ig*:minted:gp_makers}
\end{figure}
%
The data reduction step includes all tasks required to process and prepare
\gammaray data from the DL3 level to modeling and fitting. The \code{gammapy.makers} sub-package
contains the various classes and functions required to do so. First, events are
binned and IRFs are interpolated and projected onto the chosen analysis
geometry. This produces counts, exposure, background, psf and energy dispersion
maps. The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.

Because the background models suffer from strong uncertainties it is required
to correct them from the data themselves. Several techniques are commonly used
in gamma-ray astronomy such as field-of-view background normalization or
background measurement in reflected regions regions, see~\cite{Berge07}.
Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
\code{ReflectedRegionsBackgroundMaker} are in charge of this step.

>>>>

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
    \import{code-examples/generated/}{gp_makers}
	\caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
		\code{MapDataset}. All \code{Maker} classes take
        the configuration on initialisation of the class.
    }
	\label{ig*:minted:gp_makers}
\end{figure}
%
The data reduction step includes all tasks required to process and prepare
\gammaray data from the DL3 level to modeling and fitting. The \code{gammapy.makers} sub-package
contains the various classes and functions required to do so. First, events are
binned and IRFs are interpolated and projected onto the chosen analysis
geometry. This produces counts, exposure, background, psf and energy dispersion
maps. The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.

Because the background models suffer from strong uncertainties it is required
to correct them from the data themselves. Several techniques are commonly used
in \gammaray astronomy such as field-of-view background normalization or
background measurement in reflected regions, see~\cite{Berge07}.
Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
\code{ReflectedRegionsBackgroundMaker} are in charge of this step.
